---
title: "01_data_merging"
author: "Johannes Renz"
date: "2024-02-05"
output: html_document
---

```{r, echo=FALSE, include=FALSE}
rm(list=ls())

libs <- c ("dplyr", "stringdist", "stringr", "ggplot2", "openxlsx", "haven", "data.table", "tidyr", "fixest", "ggplot2", "plm", "lubridate", "anytime", "remotes", "did", "git2r", "httr", "tools", "base64enc")
libs_to_install <- libs[!(libs %in% installed.packages())]
sapply(libs_to_install, install.packages, character_only = TRUE)
sapply(libs, library, character.only = TRUE)


ceo_dismissal<-read_dta("//vmpfs-int/ag-int$/05_Forschungsprojekte/AliRenz/analysis/rawdata/CEODismissal/CEO Dismissal Database Posted to Web 9Nov23.dta")


crsp<-fread("//vmpfs-int/ag-int$/05_Forschungsprojekte/AliRenz/analysis/rawdata/WRDS/crsp_99.csv")

execucomp<-fread("//vmpfs-int/ag-int$/05_Forschungsprojekte/AliRenz/analysis/rawdata/WRDS/comp_execucomp.csv")


boardex<-fread("//vmpfs-int/ag-int$/05_Forschungsprojekte/AliRenz/analysis/rawdata/WRDS/boardex.csv")



```

select relevant ranges and variables from datasets

```{r}

execucomp<-execucomp%>%
  select(GVKEY, #company identifier
         YEAR, #year
         SIC, #industry
         SPCODE, # SP-> SP500, SM-> smallcap, MD -> midcap, EX -> not in S&P INDEX
         TICKER, #stockticker
         EXEC_FULLNAME, # full exec name
         CEOANN,# identifies exec who held ceo that year
         EXECID, # executive ID number
         GENDER, #CEO gender
         PAGE, #present age
         CO_PER_ROL, # gives unique CEO company combination
         AGE, #CEO AGE
         SHROWN_EXCL_OPTS_PCT, # percentage of shares owned by ceo excluding options if greater than 1%
  )

execucomp<-subset(execucomp, execucomp$YEAR>=1998)
execucomp<-subset(execucomp, execucomp$CEOANN=="CEO")



crsp<-crsp%>%
  select(GVKEY, # company identifier
         fyear, # year
         conm, # nompany name
         tic, #ticker
         weburl, #WEB URL
         prcc_c, #closing price, annual
         at #firm size
  )


crsp$year<-crsp$fyear
names(execucomp)[names(execucomp)=="YEAR"]<-"year"
crsp<-subset(crsp,crsp$year>=1998)

filter<-crsp%>%group_by(GVKEY, year)%>%filter(n()>1) # some double obs, but same values (check with this filter df)
crsp<-crsp%>%
  group_by(GVKEY, year)%>%
  slice_head(n=1) #deal with double obs


names(ceo_dismissal)[names(ceo_dismissal)=="gvkey"]<-"GVKEY"
names(ceo_dismissal)[names(ceo_dismissal)=="co_per_rol"]<-"CO_PER_ROL"



filter<-ceo_dismissal%>%group_by(CO_PER_ROL, fyear)%>%filter(n()>1) # some double obs, but same values

ceo_dismissal<-subset(ceo_dismissal, fyear>=1998)


boardex<-boardex%>%
  select(
    BoardID, #Board ID
    DirectorID, #Director ID
    RoleName, # Role of Board member
    GenderRatio, #Gender Ratio of Board
    AnnualReportDate,#report date / year var
    Ticker #ticker
  )

```

Generate board level variables

```{r}

boardex_post<-boardex%>%
  mutate(# get year variable
        year=year(AnnualReportDate), 
        # generate duality variable (CEO member of board)
         duality=as.integer(grepl("CEO", RoleName, fixed=TRUE)))%>% 
  # aggregate to firm year level
  group_by(Ticker, year)%>% 
    summarize(
      gender_ratio=mean(GenderRatio, na.rm=TRUE), 
      #mean or first does not matter, since it returns the same values
      duality=max(duality, na.rm=TRUE),
      #board size is number of registered directors:
      board_size=n(),
            # just to deal with the column and retain it, again it does not matter if its first or last, all are consistent anyways
      TICKER=first(Ticker),
      .groups="drop")


```

Run merges

```{r}

ceo_dismissal$year<-ceo_dismissal$fyear

df<-left_join(execucomp, crsp, by=c("GVKEY", "year"))

df<-left_join(df, ceo_dismissal, by=c("CO_PER_ROL", "fyear"))

names(df)[names(df)=="year.x"]<-"year"
df<-left_join(df, boardex_post, by=c("TICKER", "year"))


sum(is.na(df$TIC))
if (sum(df$TIC!=df$TICKER)!=0){stop("TICKERS UNMATCHED")} # throw error for inconsistent tickers, just to double check the gvkey and co_per_rol joins

```

load glassdoor data

```{r}

rm(list=setdiff(ls(), "df")) #drop all intermediate dfs

reviews<-fread("//fs2019-02/revelio$/analysis/newdata/reviews_eng_usa_clean.csv") 

```

handle glassdoor data, generate numerical ceo rating

```{r}

reviews<-reviews%>%
  select(year,company,rating_overall,rating_senior_leadership,rating_ceo,ticker, website)

reviews$ceo_approve=ifelse(reviews$rating_ceo=="APPROVE",1,0)
reviews$ceo_disapprove<-ifelse(reviews$rating_ceo=="DISAPPROVE",1,0)
reviews$ceo_rating<-reviews$ceo_approve-reviews$ceo_disapprove
#this is the same as including no opinion as speerate ifelse, since all non approve or disapprove are no opinions

reviews<-reviews%>%select(-rating_ceo, -ceo_approve, -ceo_disapprove)
#drop uneccessary intermediate columns

```

aggregate reviews to firm year level

```{r}

reviews_aggregated<-reviews%>%
  group_by(ticker, year)%>%
  summarise(across(where(is.numeric), ~mean(.)),
            across(where(is.character), ~first(.)), #character columns are not used anyway, but are sometimes interesting for troubleshooting
            n_obs = n(),
            .groups="drop")

```



```{r}

df<-df%>%mutate(merge_id=row_number()) #number generated to keep track and filter matches

names(df)[names(df)=="year.x"]<-"year"
names(df)[names(df)=="tic"]<-"ticker"

#step 1: ticker matches

panel1<-inner_join(df, reviews_aggregated, by=c("ticker", "year"))#this is the main glassdoor-df merge

sum(!is.na(panel1$ceo_rating)) #just some checks 
sum(panel1$website!=panel1$website.y) #same, just to see that websites match



#step2 website matches

leftovers<-anti_join(df, panel1, by=c("ticker", "year"))#this gets all unmatched columns

names(leftovers)[names(leftovers)=="weburl"]<-"website"


panel2<-inner_join(leftovers, reviews_aggregated, by=c("website", "year"))#this matches exact website matches

panel_merged<-rbind(panel1, panel2, fill=TRUE)#binds both matched panels together


#step3 merge both based on merging keys
cols<-colnames(reviews_aggregated)
cols<-c(cols, "merge_id")

panel_merged <- panel_merged[, ..cols, drop = FALSE]


panel<-left_join(df, panel_merged, by="merge_id")






```



```{r}

panel$female=ifelse(panel$GENDER=="FEMALE",1,0)
panel$male=ifelse(panel$GENDER=="MALE",1,0)

sum(panel$female)


filter<-panel%>%group_by(GVKEY.x, year.x)%>%filter(n()>1) # some double obs, but same values

panel<-panel%>%
  group_by(GVKEY.x, year.x)%>%
  slice_head(n=1)



```



```{r}

rm(list=setdiff(ls(), "panel")) #drop all intermediate dfs
gc() #free up memory

df<-panel

names(df)[names(df)=="GVKEY.x"]<-"gvkey"
names(df)[names(df)=="year.x"]<-"year"

```

this cell just double checks that the ceo_dismissal database runs synchronous to execucomp

```{r}

df<-df%>%arrange(gvkey,year)%>%
  group_by(gvkey)%>%
  mutate(
    EXECID_lag=dplyr::lag(EXECID, n=1),
   departure_code_tcor=dplyr::lag(departure_code, n=1),#departure codes are coded in the year of departure, not the turnover year, which is the following
   ceo_dismissal_tcor=lag(ceo_dismissal, n=1)
  )
# calculate the turnover
df$ceo_change <- ifelse(!is.na(df$departure_code_tcor), 1, 0)
df$ceo_change[df$departure_code_tcor %in% c(7, 8, 9)] <- 0

table(df$ceo_change)

sum(df$ceo_change, na.rm=TRUE)
print("both")
sum(!is.na(df$departure_code_tcor)&df$ceo_change==1)
print("only execucomp")
sum(!is.na(df$departure_code_tcor)&df$ceo_change==0)
print("only dds")
sum(is.na(df$departure_code_tcor)&df$ceo_change==1)
print("neither")
sum(is.na(df$departure_code_tcor)&df$ceo_change==0) 

uniqueN(df$gvkey)
uniqueN(df$co_pre_rol)
df<-df[order(df$gvkey, df$year),]

df<-df%>%select(-notes,-sources,-eight_ks) #enconding issues when exporting

```

generate estimation related variables

```{r}

df<-df%>%
  group_by(gvkey)%>%
  mutate(
    prcc_c_lag=dplyr::lag(prcc_c, n=1),
    return=((prcc_c-prcc_c_lag)/prcc_c_lag),
    #total weights (not used in replication, but some other commands require specification like this)
    weights=sum(n_obs, na.rm=TRUE),
    #mean weights (these are used later)
    weights_adj=floor(mean(n_obs, na.rm=TRUE)) 
    )

df<-subset(df, year>=2000)
```

export dataset

```{r}

df<-df%>%
  select(-coname)#encoding issues

write.csv(df,"//vmpfs-int/ag-int$/05_Forschungsprojekte/AliRenz/analysis/tmp/base_panel.csv")

```

prepare industry returns for merging in STATA (final merging done in stata, because ffind command exists in STATA to classify industries accorign to the classification used.)

Note that due to weird data formatting, some data processing was already done by hand

```{r}

ind_ret<-read.csv("//vmpfs-int/ag-int$/05_Forschungsprojekte/AliRenz/analysis/rawdata/industry_returns/12_Industry_Portfolios_Wout_Div.csv",sep=",")

ind_ret<-ind_ret[1:96, ]#weighted


ind_ret<-ind_ret%>%
  pivot_longer(cols = setdiff(colnames(ind_ret), "year"), names_to= "industry", values_to = "ind_return" ) #pivot to long

#clean double spaces
ind_ret[] <- lapply(ind_ret, function(x) gsub(" ", "", x))

ind_ret<-subset(ind_ret, year>=2000)

#convert to numeric columns
ind_ret$industry<-as.numeric(sub("X", "", ind_ret$industry))
ind_ret$year<-as.numeric(ind_ret$year)

write_dta(ind_ret,"//vmpfs-int/ag-int$/05_Forschungsprojekte/AliRenz/analysis/tmp/industry_returns.dta")

```