---
title: "Webscraping ECB"
author: "Johannes Renz"
date: "2023-06-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This R Script scrapes all Press Releases by the ECB as well as Speeches by President, Vice President and Board Members of the ECB. Dates and Headlines are also mostly collected. The Scraping takes about 30 Minutes. Following this, an initial dictionary-based analysis is done. Details are in the submitted paper.

Outcome datasets that will be saved for further analysis should be:
- docs_trim, 125000 obs, 1 var (for BERTopic)
- results_trim, 5500 obs, 6 var (for relatio)
- inequality_dict_df,  45 obs, 2 var (for Paper directly)


Outcome datasets that will not be saved for dictionary analysis should be:
- docs_trim, 125000 obs, 2 var (was used to check specific documents´ result from the dictionary)

load packages, clear memory and setwd
```{r}
rm(list=ls())
library(kableExtra)
library(dplyr)
library(rvest)
library(tidyr)
library(tidyverse) 
library(stringr) 
library(tidytext) 
library(textdata)
library(progress)
library(xtable)
setwd("/Users/johannesrenz/Library/Mobile Documents/com~apple~CloudDocs/Uni/Comp Text")
``` 




This cell scrapes all entries from all press statement subsections, as well as speeches subsections. Links are filtered for English language only.

```{r}
links_list<- c("https://www.ecb.europa.eu/press/pr/activities/ecb/html/index.en.html",
               "https://www.ecb.europa.eu/press/pr/activities/mopo/html/index.en.html",
               "https://www.ecb.europa.eu/press/pr/activities/stats/html/index.en.html",
                "https://www.ecb.europa.eu/press/pr/activities/paym/html/index.en.html",
                "https://www.ecb.europa.eu/press/pr/activities/prud/html/index.en.html",
                "https://www.ecb.europa.eu/press/pr/activities/intco/html/index.en.html",
                "https://www.ecb.europa.eu/press/pr/activities/bc/html/index.en.html",
                "https://www.ecb.europa.eu/press/pr/activities/legal/html/index.en.html",
                "https://www.ecb.europa.eu/press/pr/activities/ssm/html/index.en.html",
                "https://www.ecb.europa.eu/press/pr/activities/others/html/index.en.html",
               "https://www.ecb.europa.eu/press/key/speaker/bm/html/index.en.html",
               "https://www.ecb.europa.eu/press/key/speaker/vicepres/html/index.en.html",
               "https://www.ecb.europa.eu/press/key/speaker/pres/html/index.en.html")



all_links <- character()  # Create an empty character vector to store the links

for (i in seq_along(links_list)) {
  page <- read_html(links_list[i])
  links <- page %>%
    html_nodes(".arrow") %>%
    html_attr("href")
  
  all_links <- c(all_links, links)  # Concatenate the links with the existing vector
}

# Filter for English
all_links <- all_links[grep("en.html$", all_links)]

```

This cell scrapes the content from the links that were just extracted. This is split into two parts, because of timeouts with the requests. 

```{r}

l<- length(all_links)
l2<- l/2
all_links_1<-all_links[1:l2-1]
all_links_2<-all_links[l2:l]


# Create empty df
results_1 <- data.frame(link = character(),
                      publicationdate = character(),
                      publicationdate_old = character(),
                      title = character(),
                      sectionp = character(),
                      #summary = character(),
                      stringsAsFactors = FALSE)

# Get the total number of links
total_links <- length(all_links_1)

# Initialize progress bar
pb <- progress_bar$new(total = total_links, format = "[:bar] :percent :eta")

# Iterate over links
for (i in seq_along(all_links_1)) {
  link <- all_links[i]

  # Complete URL
  full_url <- paste0("https://www.ecb.europa.eu", link)

  # Read the press statement page
  press_page <- read_html(full_url)

  # Extract sections
  publication_date <- press_page %>% html_node(".ecb-publicationDate") %>% html_text()
  publication_date_old <- press_page %>% html_node(".ecb-pressContentPubDate") %>% html_text()
  title <- press_page %>% html_node("h1") %>% html_text()

  # Handle section and summary extraction
  section <- NA
  summary <- NA
  section_nodes <- press_page %>% html_nodes(".section p")
  if (length(section_nodes) > 0) {
    section <- section_nodes %>% html_text() %>% paste(collapse = " ")
    summary_nodes <- press_page %>% html_nodes(".section li")
    if (length(summary_nodes) > 0) {
      summary <- summary_nodes %>% html_text() %>% paste(collapse = " ")
    }
  }

  # Bind rows
  row <- data.frame(link = full_url,
                    publicationdate = publication_date,
                    publicationdate_old = publication_date_old,
                    title = title,
                    sectionp = section,
                    #summary = summary,
                    stringsAsFactors = FALSE)

  results_1 <- rbind(results_1, row)
  
  # Update progress bar
  pb$tick()
}

#close progess bar
pb$terminate()
```

Second half (Basically same Code as before):

```{r}

# Create empty df
results_2 <- data.frame(link = character(),
                      publicationdate = character(),
                      publicationdate_old = character(),
                      title = character(),
                      sectionp = character(),
                      #summary = character(),
                      stringsAsFactors = FALSE)

# Get the total number of links
total_links <- length(all_links_2)

# Initialize progress bar
pb <- progress_bar$new(total = total_links, format = "[:bar] :percent :eta")

# Iterate over links
for (i in seq_along(all_links_2)) {
  link <- all_links[i]

  # Complete URL
  full_url <- paste0("https://www.ecb.europa.eu", link)

  # Read the press statement page
  press_page <- read_html(full_url)

  # Extract sections
  publication_date <- press_page %>% html_node(".ecb-publicationDate") %>% html_text()
  publication_date_old <- press_page %>% html_node(".ecb-pressContentPubDate") %>% html_text()
  title <- press_page %>% html_node("h1") %>% html_text()

  # Handle section and summary extraction
  section <- NA
  summary <- NA
  section_nodes <- press_page %>% html_nodes(".section p")
  if (length(section_nodes) > 0) {
    section <- section_nodes %>% html_text() %>% paste(collapse = " ")
    summary_nodes <- press_page %>% html_nodes(".section li")
    if (length(summary_nodes) > 0) {
      summary <- summary_nodes %>% html_text() %>% paste(collapse = " ")
    }
  }

  # Bind rows
  row <- data.frame(link = full_url,
                    publicationdate = publication_date,
                    publicationdate_old = publication_date_old,
                    title = title,
                    sectionp = section,
                    #summary = summary,
                    stringsAsFactors = FALSE)

  results_2 <- rbind(results_2, row)
  
  # Update progress bar
  pb$tick()
}

#close progess bar
pb$terminate()


```

This cell concats the two dataframes, drops unwanted observations and tries to get a date for all obs

```{r}

results<-rbind(results_1,results_2)

#fill column of publ date with old html coded publ date
results_trim$publicationdate[is.na(results_trim$publicationdate)]<-results_trim$publicationdate_old[is.na(results_trim$publicationdate)]

#remove leading space, otherwise asDate is confused
results_trim$publicationdate <- trimws(results_trim$publicationdate)

#change date format
results_trim$date <- as.Date(results_trim$publicationdate, format = "%d %B %Y")
results_trim$date <- format(results_trim$date, "%m-%Y")


```

This cell saves the results.

```{r}

write.csv(results_trim, file="ecb_full_scrape_03.csv")

```

This cell scrapes the paragraph form for BERTopic Topic analysis. 

```{r}

#create empty df
docs <- data.frame(sectionp = character(),
                      stringsAsFactors = FALSE)

# Initialize progress bar
pb <- progress_bar$new(total = length(all_links), format = "[:bar] :percent :eta")

# iterate over links
for (link in all_links) {
  #complete URL
  full_url <- paste0("https://www.ecb.europa.eu", link)
  
  #read the speeches page
  press_page <- read_html(full_url)
  
  #extract section
  section <- press_page %>% html_nodes(".section p") %>% html_text()
  
  #bind rows
  row <- data.frame(sectionp = section,
                    stringsAsFactors = FALSE)
  
  docs <- rbind(docs, row)

 # Update progress bar
  pb$tick()
}

#close progess bar
pb$terminate()

#remove obs with only notes to graphics or *** by character length , false positive limited, since we only want to look at paragraphs of speeches

docs_trim <- docs[nchar(docs$sectionp) >= 50, , drop = FALSE]


write.csv(docs_trim, file="docs_ecb_scrape.csv")

```


Initial Analysis with dictionaries: Words related to inequality are checked for how often they arise in the dataset.

```{r}

#define dictionary

ineq_dict <- c('inequality', 'inequal', 'redistribution', 'redistribute','wealth gap', 'income disparity', 'social inequality', 'economic disparity', 'poverty', 'affluence', 'social mobility', 'socioeconomic divide', 'wage inequality', 'class divide', 'marginalized', 'underprivileged', 'social justice', 'disadvantaged', 'unequal', 'disparity', 'top 1%', 'wealth distribution','wealth concentration', 'income gap', 'economic injustice', 'regressive taxation','inclusive growth', 'inclusive prosperity', 'structural inequality', 'intergenerational poverty','wealth redistribution', 'opportunity gap', 'wealth inequality', 'income inequality', 'financial inequality', 'economic mobility', 'inequality reduction', 'fairness', 'distribution of wealth', 'distribution of income', 'gap between rich and poor')


# Function to count word occurrences in a text
count_occurrences <- function(text, words) {
  word_counts <- sapply(words, function(word) sum(grepl(word, text, ignore.case = TRUE)))
  total_words <- length(unlist(strsplit(text, "\\s+")))
  word_percentages <- word_counts / total_words * 100
  data.frame(Word = words, Absolute_Count = word_counts, Relative_Percentage = word_percentages, stringsAsFactors = FALSE)
}


# Apply the function to the Text column in the data frame
inequality_dict_df <- count_occurrences(docs_trim$sectionp, ineq_dict)

# Calculate the sum of absolute counts and relative percentages
sum_absolute_counts <- sum(inequality_dict_df$Absolute_Count)
sum_relative_percentages <- sum(inequality_dict_df$Relative_Percentage)


# Create a vectorized function to count dictionary words in each observation
count_dictionary_words <- function(text, words) {
  text <- tolower(text)  # Convert the text to lowercase
  words <- tolower(words)  # Convert the dictionary words to lowercase
  word_counts <- sapply(words, function(word) sum(str_detect(text, paste0("\\b", word, "\\b"))))
  total_count <- sum(word_counts)
  return(total_count)
}

# Apply the function to the Text column in the data frame
docs_trim$dict_count <- sapply(docs_trim$sectionp, count_dictionary_words, words = ineq_dict)
```

This Cell saves the output into tex form.

```{r}
#output and save the dictionary with counts to tex format:

#Reset Index and keep only relevant columns
ineq_dic_out<- data.frame(Index = 1:nrow(inequality_dict_df), inequality_dict_df, row.names = NULL)
ineq_dic_out <- subset(ineq_dic_out, select = c(Word,Absolute_Count))

#Add a sum at the bottom
sum_row <- ineq_dic_out %>%
  summarize(Word = "Total", Absolute_Count = sum(Absolute_Count))
ineq_dic_out <- bind_rows(ineq_dic_out, sum_row)
print(xtable(ineq_dic_out, type = "latex"), file = "ineq_dic.tex")

```

FEDERAL RESERVE DATASET

```{r}

links_list<- c("https://www.federalreserve.gov/newsevents/pressreleases/2022-press.htm",
               "https://www.federalreserve.gov/newsevents/pressreleases/2021-press.htm",
               "https://www.federalreserve.gov/newsevents/pressreleases/2020-press.htm",
               "https://www.federalreserve.gov/newsevents/pressreleases/2019-press.htm",
               "https://www.federalreserve.gov/newsevents/pressreleases/2018-press.htm",
               "https://www.federalreserve.gov/newsevents/pressreleases/2017-press.htm",
               "https://www.federalreserve.gov/newsevents/pressreleases/2016-press.htm",
               "https://www.federalreserve.gov//newsevents/pressreleases/2015all.htm",
               "https://www.federalreserve.gov//newsevents/pressreleases/2014all.htm",
               "https://www.federalreserve.gov//newsevents/pressreleases/2013all.htm",
               "https://www.federalreserve.gov//newsevents/pressreleases/2012all.htm",
               "https://www.federalreserve.gov//newsevents/pressreleases/2011all.htm",
               "https://www.federalreserve.gov//newsevents/pressreleases/2010all.htm",
               "https://www.federalreserve.gov//newsevents/pressreleases/2009all.htm",
               "https://www.federalreserve.gov//newsevents/pressreleases/2008all.htm",
               "https://www.federalreserve.gov//newsevents/pressreleases/2007all.htm",
               "https://www.federalreserve.gov//newsevents/pressreleases/2006all.htm"
               
               )

# Create an empty data frame to store the data
fed_links_df <- data.frame(time = character(), link = character(), stringsAsFactors = FALSE)

for (i in seq_along(links_list)) {
  page <- read_html(links_list[i])
  
  times <- page %>%
    html_nodes(".eventlist__time time") %>%
    html_text()
  
  links <- page %>%
    html_nodes(".eventlist__event a") %>%
    html_attr("href")
  
  # Create a data frame for the current page
  current_df <- data.frame(time = times, link = links, stringsAsFactors = FALSE)
  
  # Append the current data frame to the main data frame
  fed_links_df <- rbind(fed_links_df, current_df)
}



```


```{r}

#create empty df
docs <- data.frame(sectionp = character(),
                      stringsAsFactors = FALSE)

fed_links = as.list(fed_links_df$link)

# Initialize progress bar
pb <- progress_bar$new(total = length(fed_links), format = "[:bar] :percent :eta")

# iterate over links
for (link in fed_links) {
  #complete URL
  full_url <- paste0("https://www.federalreserve.gov", link)
  
  #read the speeches page
  press_page <- read_html(full_url)
  
  #extract section
  section <- press_page %>% html_nodes("#article p") %>% html_text()
  
  #bind rows
  row <- data.frame(sectionp = section,
                    stringsAsFactors = FALSE)
  
  docs <- rbind(docs, row)

 # Update progress bar
  pb$tick()
}

#close progess bar
pb$terminate()


```